The Evolution of Phenotypically Invariant Genetic Networks

### 2018-01-18 kalman_walk_paper.tex
minor edits

It is not a new observation that there is often more than one way to do the same thing,
and that this may lead to speciation or that speciation can be the result of neutral and quasi-neutral processes \citep{wright1932roles, nei1983models, barton1989divergence, barton2001role, gavrilets2004fitness}.
Incompatibilities between distinct genotypes encoding identical phenotypes can
even persist stably within a species \citep{phillips1996maintenance}.
For instance, \citet{tulchinsky2014hybrid}
%(and similarly \citet{khatri2015simple})
looked for hybrid incompatibility
following regulatory sequence drift,
and \citet{porter2002speciation} studied speciation in populations expressing a simple regulatory cascade.
Both found rapid speciation following directional selection,
but only equivocal support for speciation under models of purely neutral drift.
%Additionally, \citet{fierst} observed speciation due to an increase of segregation variance under balancing selection, in models of weak to moderate, but not strong epistasis.
Our model differs from previous work in that we use linear systems theory
to both explore a much richer class of regulatory network models,
and provide analytical expectations in large populations with complex phenotypes
that would be inaccessible to population simulations.
%REFERENCE: Barton's paper (PETER). \citep{barton2010natural}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}

>>>>

It is not a new observation that there is often more than one way to do the same thing, or that speciation can be the result of neutral and quasi-neutral processes \citep{wright1932roles, nei1983models, barton1989divergence, barton2001role, gavrilets2004fitness}.
%Incompatibilities between distinct genotypes encoding identical phenotypes can
%even persist stably within a species \citep{phillips1996maintenance}.
For instance, \citet{tulchinsky2014hybrid}
%(and similarly \citet{khatri2015simple})
looked for hybrid incompatibility
following regulatory sequence drift,
and \citet{porter2002speciation} studied speciation in populations expressing a simple regulatory cascade.
Both found rapid speciation following directional selection,
but only equivocal support for speciation under models of purely neutral drift.
%Additionally, \citet{fierst} observed speciation due to an increase of segregation variance under balancing selection, in models of weak to moderate, but not strong epistasis.
Our model differs from previous work in that we use linear systems theory
to both explore a much richer class of regulatory network models,
and provide analytical expectations in large populations with complex phenotypes
that would be inaccessible to population simulations.
%REFERENCE: Barton's paper (PETER). \citep{barton2010natural}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}
